The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-22 paper/paper.tex
paper: fix minor errors in conclusion
paper: fix typesetting a pi
A few mmore typos

So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
\begin{align*}
  \framep[n][p]             & : \U                                               & \mbox{for all $p\leq n$} \\
  \painting[n][p]           & : \framep[n][p] \rightarrow \U                     & \mbox{for all $p\leq n$} \\
  \restrf[n][p]             & : \Pi q \leq n-p.\, Pi \epsilon.\, \framep[n+1][p]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)
  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                                      \\
\end{align*}
which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
\begin{align*}
  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)                                                                    \\
\end{align*}

@@

\begin{align*}
  \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
  \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
  \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n-1 \rbrack]
  \left(
  \begin{array}{l}
      \framep[n][\lbrack 0,n \rbrack]   \\
      \painting[n][\lbrack 0,n \rbrack] \\
    \end{array}\right)                                                                                                                                                          \\
  \deps[n][\lbrack 0,n \rbrack]                                                                        & \defeq &
  \left(
  \begin{array}{l}
      \framep[n][\lbrack 0,n \rbrack]   \\
      \painting[n][\lbrack 0,n \rbrack] \\
      \restrf[n][\lbrack 0,n \rbrack]   \\
    \end{array}\right)                                                                                                                                                          \\
  \fulldeps[n](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U)                      & \defeq &
  \left(
  \begin{array}{l}
      \deps[n][\lbrack 0,n \rbrack] \\
      E                             \\
    \end{array}\right)                                                                                                                                                              \\
  \restrp[n][\lbrack 0,n \rbrack](E)                                                                   & :      & \restrptype[n][\lbrack 0,n \rbrack]
  (\fulldeps[n](E))                                                                                                                                                                          \\
  \cohf[n][\lbrack 0,n \rbrack](E)                                                                     & :      & \cohftype[n][\lbrack 0,n \rbrack]
  \left(
  \begin{array}{l}
      \fulldeps[n](E)                    \\
      \restrp[n][\lbrack 0,n \rbrack](E) \\
    \end{array}\right)                                                                                                                                                         \\
  \depscohs[n][\lbrack 0,n \rbrack](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U) & \defeq &
  \left(
  \begin{array}{l}
      \fulldeps[n](E)                    \\
      \restrp[n][\lbrack 0,n \rbrack](E) \\
      \cohf[n][\lbrack 0,n \rbrack](E)   \\
    \end{array}\right)                                                                                                                                                         \\
  \fulldepscohs[n]
  \left(\begin{array}{l}
            E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                        \\
            E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
          \end{array}\right)          & \defeq &
  \left(
  \begin{array}{l}
      \depscohs[n][\lbrack 0,n \rbrack](E) \\
      E'                                   \\
    \end{array}\right)                                                                                                                                                       \\
  \cohp[n][\lbrack 0,n-1 \rbrack](E)(E')                                                               & :      & \cohptype[n][\lbrack 0,n \rbrack]
  (\fulldepscohs[n](E)(E'))                                                                                                                                                                  \\
\end{align*}

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack]$.
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
  \item $\depscoht[n][\lbrack 0,n+1 \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\restrp[n][\lbrack 0,n \rbrack](E)$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n](E)(E')$, $\cohp[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
\end{itemize}

Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n+1][\lbrack 0,n+1 \rbrack]) \rightarrow \U$. This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.

>>>>

So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
\begin{align*}
  \framep[n][p]             & : \U                                                & \mbox{for all $p\leq n$} \\
  \painting[n][p]           & : \framep[n][p] \rightarrow \U                      & \mbox{for all $p\leq n$} \\
  \restrf[n][p]             & : \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)
  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                                       \\
\end{align*}
which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
\begin{align*}
  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)                                                                    \\
\end{align*}

@@

\begin{align*}
  \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n \rbrack]                                       \\
  \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n \rbrack](\framep[n][\lbrack 0,n \rbrack]) \\
  \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n \rbrack]
  \left(
  \begin{array}{l}
      \framep[n][\lbrack 0,n \rbrack]   \\
      \painting[n][\lbrack 0,n \rbrack] \\
    \end{array}\right)                                                                                                                                                          \\
  \deps[n][\lbrack 0,n \rbrack]                                                                        & \defeq &
  \left(
  \begin{array}{l}
      \framep[n][\lbrack 0,n \rbrack]   \\
      \painting[n][\lbrack 0,n \rbrack] \\
      \restrf[n][\lbrack 0,n \rbrack]   \\
    \end{array}\right)                                                                                                                                                          \\
  \fulldeps[n](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U)                      & \defeq &
  \left(
  \begin{array}{l}
      \deps[n][\lbrack 0,n \rbrack] \\
      E                             \\
    \end{array}\right)                                                                                                                                                              \\
  \restrp[n][\lbrack 0,n \rbrack](E)                                                                   & :      & \restrptype[n][\lbrack 0,n \rbrack]
  (\fulldeps[n](E))                                                                                                                                                                          \\
  \cohf[n][\lbrack 0,n \rbrack](E)                                                                     & :      & \cohftype[n][\lbrack 0,n \rbrack]
  \left(
  \begin{array}{l}
      \fulldeps[n](E)                    \\
      \restrp[n][\lbrack 0,n \rbrack](E) \\
    \end{array}\right)                                                                                                                                                         \\
  \depscohs[n][\lbrack 0,n \rbrack](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U) & \defeq &
  \left(
  \begin{array}{l}
      \fulldeps[n](E)                    \\
      \restrp[n][\lbrack 0,n \rbrack](E) \\
      \cohf[n][\lbrack 0,n \rbrack](E)   \\
    \end{array}\right)                                                                                                                                                         \\
  \fulldepscohs[n]
  \left(\begin{array}{l}
            E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                           \\
            E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack](E)))\rightarrow \U \\
          \end{array}\right)       & \defeq &
  \left(
  \begin{array}{l}
      \depscohs[n][\lbrack 0,n \rbrack](E) \\
      E'                                   \\
    \end{array}\right)                                                                                                                                                       \\
  \cohp[n][\lbrack 0,n \rbrack](E)(E')                                                               & :      & \cohptype[n][\lbrack 0,n \rbrack]
  (\fulldepscohs[n](E)(E'))                                                                                                                                                                  \\
\end{align*}

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$.
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
  \item $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
\end{itemize}

Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$. This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.
